Overlooked Dynamics in Algorithmic Recourse

### 2022-07-12 dev/resources/misc/boston_housing.qmd
setting up Julia framework

```{julia}
include("../src/load.jl")
using AlgorithmicRecourse, MLDatasets, Flux
using Plots, PlotThemes
theme(:juno)
using Logging
disable_logging(Logging.Info)
output_folder = "output/boston_housing"
www_folder = "www/boston_housing"
using DataFrames, CSV
using BSON: @save, @load
using Base.Filesystem: joinpath
```

@@

Prepare ensemble for use with AlgorithmicRecourse.jl:

>>>>

```{julia}
include("../src/load.jl")
using CounterfactualExplanations, MLDatasets, Flux
using Plots, PlotThemes
theme(:juno)
using Logging
disable_logging(Logging.Info)
output_folder = "output/boston_housing"
www_folder = "www/boston_housing"
using DataFrames, CSV
using BSON: @save, @load
using Base.Filesystem: joinpath
```

@@

Prepare ensemble for use with CounterfactualExplanations.jl:

### 2022-07-12 notebooks/synthetic.qmd
setting up Julia framework

---
title: Synthetic data
jupyter: julia-1.6
---

@@

```{julia}
include("src/load.jl")
using CounterfactualExplanations, Flux, Plots, PlotThemes, Random, BayesLaplace, LinearAlgebra
using Base.Filesystem: joinpath
theme(:wong)
using Logging
disable_logging(Logging.Info)
output_path = "dev/work/output/synthetic"
www_path = "dev/work/www/synthetic"
```

>>>>

---
title: Experiments with Synthetic Data
jupyter: julia-1.7
---

@@

```{julia}
include("src/AlgorithmicRecourseDynamics.jl")
using CounterfactualExplanations, Flux, Plots, PlotThemes, Random, LaplaceRedux, LinearAlgebra
theme(:wong)
output_path = output_dir("synthetic")
www_path = www_dir("synthetic")
```

### 2022-07-12 paper/sections/methodology.qmd
bleh
setting up Julia framework

[AGREE ON NOTATION]

$$
\begin{aligned}
\mathbf{s}^\prime &= \arg \min_{\mathbf{s}^\prime \in \mathcal{S}} \left(  {\left\{\ell(M(f(s_k^\prime)),t)\right\}_K}^\mathsf{T} \mathbf{1}_K + \lambda {\left\{h(f(s_k^\prime)) \right\}_K}^\mathsf{T} \mathbf{1}_K \right) \\
&= \arg \min_{\mathbf{s}^\prime \in \mathcal{S}} \left\{ \left(\ell . ((M\circ f).(\mathbf{s}^\prime),t) + \lambda (h \circ f).(\mathbf{s}^\prime)\right)^\mathsf{T} \mathbf{1}_K \right\} \\
&= \arg \min_{\mathbf{s}^\prime \in \mathcal{S}} \left\{ \sum_{k=1}^{K} {\ell(M(f(s_k^\prime)),t)}+ \lambda {h(f(s_k^\prime)) }  \right\}
\end{aligned}
$$ {#eq-general}

@@

We use 6 synthetic binary classification datasets consisting of 200-400 samples grouped in normally-distributed clusters.^[To see how the data is generated see here: [https://github.com/pat-alt/algorithmic_recourse_dynamics/blob/main/notebooks/synthetic_datasets.ipynb](https://github.com/pat-alt/algorithmic_recourse_dynamics/blob/main/notebooks/synthetic_datasets.ipynb)] The datasets are presented in @fig-synthetic-data (see also Appendix A for a formal description). Samples from the negative class are marked in blue while samples of the positive class are marked in orange.

>>>>

$$
\begin{aligned}
\mathbf{s}^\prime &= \arg \min_{\mathbf{s}^\prime \in \mathcal{S}} \left\{ \sum_{k=1}^{K} {\ell(M(f(s_k^\prime)),t)}+ \lambda {h(f(s_k^\prime)) }  \right\}
\end{aligned}
$$ {#eq-general}

@@

We use 6 synthetic binary classification datasets consisting of 200-400 samples grouped in normally-distributed clusters.^[To see how the data is generated see here: [https://github.com/pat-alt/AlgorithmicRecourseDynamics.jl/blob/main/notebooks/synthetic_datasets.ipynb](https://github.com/pat-alt/AlgorithmicRecourseDynamics.jl/blob/main/notebooks/synthetic_datasets.ipynb)] The datasets are presented in @fig-synthetic-data (see also Appendix A for a formal description). Samples from the negative class are marked in blue while samples of the positive class are marked in orange.
